### 2016-03-23 ch02-qlogms/excitation-design.tex
Different figure names per chapter
Some small things
Fix derivatives of O(2) system
 - In the text, there was a factor `s` missing
 - In the figures, the same factor was missing

 In the script, the factor was present. Now, we plot
 the derivatives from within MATLAB to doublecheck
 the plots in the thesis as well
Fix calculation of deriv in CH02

\chapter{Design of excitation signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }

@@

Direct calculations for $\damping < 1$ give
\begin{align}
\label{eq:excitation:auto}
\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega = \frac{\pi}{16\wn[1]^2}\damping^{-3} + \mathcal{O}(\damping^{-1}).
\end{align}
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
\begin{gather}
\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:excitation:cross1} \\
\leq
\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \wn[1]} 
  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.

@@

Consider the second-order subsystem with multiplicity $\multiplicity$:
\begin{equation}
  G_2(s, \theta) = \frac{\dc \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
\label{eq:excitation:secondOrderSubsystem}
\end{equation}
parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
\begin{align}
  \PartialDerivative{G_2}{\dc} 
    &= 
    \frac{G_2}{\dc}
    =
  \frac{\wn^{2\multiplicity}}{\wz}
  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
  \\
  \PartialDerivative{G_2}{\wz} 
    &= 
    \frac{-\dc \wn^{2\multiplicity}}
              {\wz} 
    \frac{s}
              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
  \\
  \PartialDerivative{G_2}{\wn} 
  &= 
  \frac{2 \dc \wn^{2\multiplicity-1} \multiplicity}
            {\wz} 
  \frac{\left( s + \wz \right) \left( s+ \damping \wn \right)}
            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \\
  \PartialDerivative{G_2}{\damping}
  &= 
  \frac{-2 \dc \wn^{2\multiplicity + 1} \multiplicity}
            {\wz}
  \frac{s \left( s + \wz \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \text{.}
\end{align}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The $3\unit{dB}$ bandwidth (\sysBW) around the peak frequency $\wM$ of the system is highlighted.}
    \label{fig:excitation:misalignment-logms}
  \end{figure}

>>>>

\chapter{Design of excitation signals}
\label{sec:excitation}
\def\thisDir{ch02-qlogms}
\tikzsetfigurename{ch02fig}
\myEpigraph{A common mistake that people make when trying to design something completely foolproof is to underestimate the ingenuity of complete fools.}{Douglas Adams}{Mostly Harmless}
\researchBasedOn{Larsson2012SYSID, Geerardyn2012IMTC, Geerardyn2013TIM, }

@@

Direct calculations for $\damping \ll 1$ give
\begin{align}
\label{eq:excitation:auto}
\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_1^{\HT}}{\partial \wn[1]}\right\}\frac{1}{\omega}\dd\omega
 = 
 \frac{\pi}
          {8\wn[1]^2}\damping^{-3} 
+ \mathcal{O}(\damping^{-1}).
\end{align}
\begin{personalNote} 
Value computed using Sage:
\begin{align*}
\frac{\pi {K}^{2}}
          {16  \sqrt{1 - \damping^2}\wn^{2} \damping^{3}} 
+
\frac{{\left(2  \damping^{2} + 1 \right)}  {K}^{2}}
         {4  \sqrt{1-\damping^{2}} \wn^{2} \damping^{2}}
+ 
\frac{{K}^{2} \arctan  
                               \left(
                                       \frac{(2  \damping^{2} - 1) \sqrt{1-\damping^{2}}}
                                                {2  (\damping^{3} - \damping)}
                              \right)}
         {8  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
\end{align*}
Remark that the latter term for $\damping \to 0$ becomes
\begin{equation}
  \frac{{K}^{2} \pi / 2}
         {8  \sqrt{1-\damping^{2}} \wn^{2}  \damping^{3}}
\end{equation}
as the argument for the $\arctan$ function tends to $\infty$.
\end{personalNote}
%
For the corresponding element in $\partial G_{1,2}$ we start by bounding the absolute value of the integral by
\begin{gather}
\left|\int_0^\infty\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\frac{1}{\omega}\dd\omega\right|
\qquad \qquad \qquad \qquad \qquad
\label{eq:excitation:cross1} \\
\leq
\int_0^\infty\left|\mathrm{Re}\left\{\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right\}\right|\frac{1}{\omega}\dd\omega
\leq \\
\qquad \qquad \qquad \qquad \qquad
\int_0^\infty\left|\frac{\partial G_1}{\partial \wn[1]}\frac{\partial G_2^{\HT}}{\partial \wn[2]}\right|\frac{1}{\omega}\dd\omega \text{.}\label{eq:excitation:cross}
\end{gather}
To proceed, consider
\begin{align}
\frac{\partial G_1}{\partial \wn[1]} 
  &= \frac{2\damping j\omega\left[1+\frac{j\omega}{\wn[1]\damping}\right]}
  {\wn[1]^2\left[1+2\frac{\damping j\omega}{\wn[1]} + \left(\frac{j\omega}{\wn[1]}\right)^2\right]^2},
\end{align}
which has zeros in $j\omega=\left\{0, \damping\wn[1]\right\}$. 
Hence $\left|\frac{\partial G_1}{\partial \wn[1]} \right|$ has asymptotic slope 20\unit{dB/\decade} for low frequencies, at $j\omega=\damping\wn[1]$ the slope increases to 40\unit{dB/\decade}. 
There are four poles which give a $-40$\unit{dB/\decade} roll-off after the peak. 
The shape of $\frac{\partial G_1}{\partial \wn[1]} $ is illustrated in \figref{fig:excitation:derivatives}.

@@

Consider the second-order subsystem with multiplicity $\multiplicity$:
\begin{equation}
  G_2(s, \theta) = \frac{\dc \wn^{2 \multiplicity} \left( s + \wz \right)}{\wz \left(s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity}}
\label{eq:excitation:secondOrderSubsystem}
\end{equation}
parametrized in $\theta =  \left[K, \wn, \wz, \damping \right]^{\T}$.
To determine the Fisher Information matrix, the derivative $\PartialDerivative{G(s,\theta)}{\theta}$ is required; its components are given by:
\begin{align}
  \PartialDerivative{G_2}{\dc} 
    &= 
    \frac{G_2}{\dc}
    =
  \frac{\wn^{2\multiplicity}}{\wz}
  \frac{s + \wz}{\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}}
  \\
  \PartialDerivative{G_2}{\wz} 
    &= 
    \frac{-\dc \wn^{2\multiplicity}}
              {\wz} 
    \frac{s}
              {\left(s^2 + 2 \damping \wn s + \wn^2\right)^{\multiplicity}} 
  \\
  \PartialDerivative{G_2}{\wn} 
  &= 
  \frac{2 \dc \wn^{2\multiplicity-1} \multiplicity}
            {\wz} 
  \frac{s \left( s + \wz \right) \left( s+ \damping \wn \right)}
            {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \\
  \PartialDerivative{G_2}{\damping}
  &= 
  \frac{-2 \dc \wn^{2\multiplicity + 1} \multiplicity}
            {\wz}
  \frac{s \left( s + \wz \right)}
             {\left( s^2 + 2 \damping \wn s + \wn^2 \right)^{\multiplicity + 1}}
  \text{.}
\end{align}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.8\columnwidth}
      \setlength\figureheight{0.5\figurewidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The $3\unit{dB}$ bandwidth ($\wdB$) around the peak frequency $\wM$ of the system is highlighted.}
    \label{fig:excitation:misalignment-logms}
  \end{figure}
